Approximation as Differentiation

### 2025-05-21 notes/biproduct.tex

\begin{definition}[Biproduct]
Suppose $\cat{C}$ a $\CMon$-enriched category. For any objects $X, Y$, the \emph{biproduct} of $X$ and $Y$ is
an object $X \biprod Y$ of $C$ together with morphisms

@@

\noindent \todo{I think we can also define ``biproduct'' just using zero morphisms, and then derive rather
than assume $\CMon$-enrichment.}

>>>>

\begin{definition}[Biproduct]
Suppose $\cat{C}$ a $\CMon$-enriched category. For any objects $X, Y$, the \emph{biproduct} of $X$ and $Y$ is
an object $X \biprod Y$ of $\cat{C}$ together with morphisms

@@
